---
title: "clean"
author: "Claire Jellison"
date: "12/27/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

TODO: 
Fix subtract the xts in clean up 
Add skew and var stuff
Add criteria for inactive campaigns
Add criteria for incomplete 1000 + 


```{r message=TRUE, warning=TRUE}
library(readr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(varhandle)
library(tidyr)
library(matrixStats)
library(gender)
library(lubridate)
```


#Clean zips 
```{r}
prepzip <- function(zips){
zips <- zips %>% 
  rename(
   urlsolid = X,
    zip = X0 
  ) 
zips
} 

zips <- prepzip(zips)
```

#Clean dhist
```{r}
prepdhist <- function(dhist){ #switch to booleans, merge with zips
dhist <- left_join(dhist, zips, by = 'urlsolid') 
dhist$is_anonymous <- str_detect(dhist$is_anonymous, fixed('True', ignore_case=TRUE)) 
dhist$verified <- str_detect(dhist$verified, fixed('True', ignore_case=TRUE))
dhist$is_offline <- str_detect(dhist$is_offline, fixed('True', ignore_case=TRUE))
dhist
} #this works now with the ignore case thing


laglead <- function(fulldf){ #add the lags and leads
fulldf <- fulldf %>% 
  arrange(created_at) %>% 
  mutate(lag1 = dplyr::lag(amount,n = 1L), lag2 = dplyr::lag(amount,n = 2L), lag3= dplyr::lag(amount,n = 3L), lag4= dplyr::lag(amount,n = 4L), lag5= dplyr::lag(amount,n = 5L), lag6 = dplyr::lag(amount,n = 6L), lag7 = dplyr::lag(amount,n = 7L), lag8= dplyr::lag(amount,n = 8L), lag9= dplyr::lag(amount,n = 9L), lag10= dplyr::lag(amount,n = 10L), alag1 = dplyr::lag(is_anonymous,n = 1L), alag2 = dplyr::lag(is_anonymous,n = 2L), alag3= dplyr::lag(is_anonymous,n = 3L), alag4= dplyr::lag(is_anonymous,n = 4L), alag5= dplyr::lag(is_anonymous,n = 5L), alag6 = dplyr::lag(is_anonymous,n = 6L), alag7 = dplyr::lag(is_anonymous,n = 7L), alag8= dplyr::lag(is_anonymous,n = 8L), alag9= dplyr::lag(is_anonymous,n = 9L), alag10= dplyr::lag(is_anonymous,n = 10L), glag1 = dplyr::lag(is_female,n = 1L), glag2 = dplyr::lag(is_female,n = 2L), glag3= dplyr::lag(is_female,n = 3L), glag4= dplyr::lag(is_female,n = 4L), glag5= dplyr::lag(is_female,n = 5L), glag6 = dplyr::lag(is_female,n = 6L), glag7 = dplyr::lag(is_female,n = 7L), glag8= dplyr::lag(is_female,n = 8L), glag9= dplyr::lag(is_female,n = 9L), glag10= dplyr::lag(is_female,n = 10L))

fulldf$alag1 <- as.integer(as.logical(fulldf$alag1)) #switches from true/false to 0/1
fulldf$alag2 <- as.integer(as.logical(fulldf$alag2))
fulldf$alag3 <- as.integer(as.logical(fulldf$alag3))
fulldf$alag4 <- as.integer(as.logical(fulldf$alag4))
fulldf$alag5 <- as.integer(as.logical(fulldf$alag5))
fulldf$alag6 <- as.integer(as.logical(fulldf$alag6))
fulldf$alag7 <- as.integer(as.logical(fulldf$alag7))
fulldf$alag8 <- as.integer(as.logical(fulldf$alag8))
fulldf$alag9 <- as.integer(as.logical(fulldf$alag9))
fulldf$alag10 <- as.integer(as.logical(fulldf$alag10))
fulldf <- fulldf %>% mutate(histavg = case_when(
  lagtype == "five" ~ (lag1 + lag2 + lag3 + lag4 + lag5)/5, 
  lagtype == "ten" | lagtype == "unknown" ~ (lag1 + lag2 + lag3 + lag4 + lag5 + lag6 + lag7 + lag8 + lag9 + lag10)/10)) %>%
  mutate(anonprop = case_when(
  lagtype == "five" ~ (alag1 + alag2 + alag3 + alag4 + alag5)/5, 
  lagtype == "ten" | lagtype == "unknown" ~ (alag1 + alag2 + alag3 + alag4 + alag5 + alag6 + alag7 + alag8 + alag9 + alag10)/10)) #%>%
  #mutate(fprop = case_when(
  #lagtype == "five" ~ (glag1 + glag2 + glag3 + glag4 + glag5)/5, 
  #lagtype == "ten" | lagtype == "unknown" ~ (glag1 + glag2 + glag3 + glag4 + glag5 + glag6 + glag7 + glag8 + glag9 + alag10)/10))

fulldf <- fulldf %>% select(-alag2, - alag3, - alag4, - alag5, -alag6, -alag7, -alag8, -alag9, -alag10, -glag2, - glag3, - glag4, - glag5, -glag6, -glag7, -glag8, -glag9, -glag10 )
  
fulldf 
}
#nts: had to run devtools::install_github("ropensci/genderdata") 
addgender <- function(dhist){ #add the gender based on first names by social security 
  firstname <- word(dhist$name, 1)
  firstname<- as.data.frame(firstname)
  dfull <- bind_cols(dhist, firstname)
  genderdf <- gender(as.character(dfull$firstname), method = "ssa") 
  genderdf$firstname <- genderdf$name
  genderdf <- distinct(genderdf) %>% select(-proportion_male, -proportion_female, -year_min, -year_max)
  finaldf <- left_join(dfull, genderdf, by = "firstname") 
  finaldf$is_female <- as.integer(str_detect(finaldf$gender, "female")) #get boolean for is female
  finaldf 
}
leaddate <- function(dhist){
  dhist <- dhist %>% mutate(createdxtslead = lead(createdxts,n = 1L))
}
fixdate <- function(date){ 
  z <- as.POSIXct(date, usetz = TRUE, format="%Y-%m-%dT%H:%M:%OS")  #look at ?strptime for documentation %Y-%m-%dT%H:%M:%S
z}
checkdateforlags <- function(dhist){  #nice this works
  dhist <- dhist %>%
  mutate(lagtype = case_when(
    createdxts <  ymd_hms("2019-06-01 01:00:00") & createdxts > ymd_hms("2016-06-01 01:00:00")  ~ "unknown",
    createdxts <  ymd_hms("2016-06-01 01:00:00")   ~ "ten",
    createdxts >  ymd_hms("2019-06-01 01:00:00")  ~ "five"
  ))
}
cleandhist <- function(dhist){
  dhist <- prepdhist(dhist)
  dhist <- dhist %>% mutate(createdxts = fixdate(created_at))
  dhist <- leaddate(dhist)
  dhist <- checkdateforlags(dhist)
  dhist <- addgender(dhist)
  dhist <- laglead(dhist)
}
```

```{r}
dhist <- cleandhist(dhist)
head(dhist,20)
nrow(dhist)
```


### Clean campattributes 

```{r}
#stuff in stringr 
#str_trim = trim leading and trailing white space 
#str_pad = pad with additional characters 
#str_detect = detects a pattern, returns TRUE/FALSE 
#str_replace = find and replace a pattern 
```

```{r}
getdigits <- function(string){
  list(regmatches(string,gregexpr("[[:digit:]]+\\.*[[:digit:]]*",string)))
}
cleanattributes <- function(dfatt){ 
  dfatt <- dfatt[ , -1]
  dfatt$goalamt <- gsub("'raised of", "", dfatt$goalamt,
     ignore.case = FALSE)
  dfatt$goalamt <- gsub("goal'", "", dfatt$goalamt,
     ignore.case = FALSE)
  dfatt$goalamt<- gsub("[[:punct:]]", "", dfatt$goalamt,  #yo you can also use str_replace if ya want
     ignore.case = FALSE)
  dfatt$amtraised<- gsub("[[:punct:]]", "", dfatt$amtraised,
     ignore.case = FALSE)
  dfatt$goalamt <- as.integer(dfatt$goalamt)
  dfatt$amtraised <- as.integer(dfatt$amtraised)
  dfatt$terminatedbool <- str_detect(dfatt$terminated, "donations") #this doesn't work? DOUBLE CHECK
  dfatt$nonprofit <- str_detect(dfatt$nonprofit., "Registered")
  dfatt<- dfatt%>% mutate(progress = amtraised/goalamt) %>% rename(urlsolid = urlname)
}
```

```{r}
campatt <- cleanattributes(campatt)
nrow(campatt)
```

#Merge important parts of dhist and campatt

```{r}
dfc <- left_join(dhist, campatt, by = "urlsolid")
dfc <- dfc %>% select(-verified, -lag2, -lag3, -lag4, -lag5, -description1, -description2, -description3, -nonprofit.)
```





fulldf$alag1 <- as.integer(as.logical(fulldf$alag1)) #switches from true/false to 0/1
fulldf$alag2 <- as.integer(as.logical(fulldf$alag2))
fulldf$alag3 <- as.integer(as.logical(fulldf$alag3))
fulldf$alag4 <- as.integer(as.logical(fulldf$alag4))
fulldf$alag5 <- as.integer(as.logical(fulldf$alag5))
fulldf$alag6 <- as.integer(as.logical(fulldf$alag6))
fulldf$alag7 <- as.integer(as.logical(fulldf$alag7))
fulldf$alag8 <- as.integer(as.logical(fulldf$alag8))
fulldf$alag9 <- as.integer(as.logical(fulldf$alag9))
fulldf$alag10 <- as.integer(as.logical(fulldf$alag10))

fulldf <- fulldf %>% mutate(histavg = case_when(
  lagtype == "five" ~ (lag1 + lag2 + lag3 + lag4 + lag5)/5, 
  lagtype == "ten" | lagtype == "unknown" ~ (lag1 + lag2 + lag3 + lag4 + lag5 + lag6 + lag7 + lag8 + lag9 + lag10)/10)) %>%
  mutate(anonprop = case_when(
  lagtype == "five" ~ (alag1 + alag2 + alag3 + alag4 + alag5)/5, 
  lagtype == "ten" | lagtype == "unknown" ~ (alag1 + alag2 + alag3 + alag4 + alag5 + alag6 + alag7 + alag8 + alag9 + alag10)/10)) %>%
  mutate(fprop = case_when(
  lagtype == "five" ~ (glag1 + glag2 + glag3 + glag4 + glag5)/5, 
  lagtype == "ten" | lagtype == "unknown" ~ (glag1 + glag2 + glag3 + glag4 + glag5 + glag6 + glag7 + glag8 + glag9 + glag10)/10))

fulldf <- fulldf %>% select( -alag2, - alag3, - alag4, - alag5, -alag6, -alag7, -alag8, -alag9, -alag10, -glag2, - glag3, - glag4, - glag5, -glag6, -glag7, -glag8, -glag9, -glag10 )
  
fulldf 
}
#it
#nts: had to run devtools::install_github("ropensci/genderdata") 
addgender <- function(dhist){ #add the gender based on first names by social security 
  firstname <- word(dhist$name, 1)
  firstname<- as.data.frame(firstname)
  dfull <- bind_cols(dhist, firstname)
  genderdf <- gender(as.character(dfull$firstname), method = "ssa") 
  genderdf$firstname <- genderdf$name
  genderdf <- distinct(genderdf) %>% select(-proportion_male, -proportion_female, -year_min, -year_max)
  finaldf <- left_join(dfull, genderdf, by = "firstname") 
  finaldf$is_female <- as.integer(str_detect(finaldf$gender, "female")) #get boolean for is female
  finaldf 
}

leaddate <- function(dhist){
  dhist <- dhist %>% 
  arrange(created_at) %>% 
  mutate(createdxtslead = lead(createdxts,n = 1L))
  
  dhist <- dhist %>% 
  mutate(timeafter = difftime(createdxts, createdxtslead, units = "secs"))

}

fixdate <- function(date){ 
  z <- as.POSIXct(date, usetz = TRUE, format="%Y-%m-%dT%H:%M:%OS")  #look at ?strptime for documentation %Y-%m-%dT%H:%M:%S
z}

checkdateforlags <- function(dhist){  #nice this works
  dhist <- dhist %>%
  mutate(lagtype = case_when(
    createdxts <  ymd_hms("2019-06-01 01:00:00") & createdxts > ymd_hms("2016-06-01 01:00:00")  ~ "unknown",
    createdxts <  ymd_hms("2016-06-01 01:00:00")   ~ "ten",
    createdxts >  ymd_hms("2019-06-01 01:00:00")  ~ "five"
  ))
}

varandskew10 <- function(dhist){
  variance <- apply(dhist[,20:29], 1, var)
  dhist$variance <- variance
  skew <- apply(dhist[,20:29], 1, skewness)
  dhist$skewness <- skew
  dhist
}

cleandhist <- function(dhist){
  dhist <- prepdhist(dhist)
  dhist <- dhist %>% mutate(createdxts = fixdate(created_at))
  dhist <- leaddate(dhist)
  dhist <- checkdateforlags(dhist)
  dhist <- addgender(dhist) #this one is sloooow
  dhist <- laglead(dhist)
  dhist <- dhist %>% group_by(urlsolid) %>% mutate(seedvalue = cumsum(amount) - amount)
}

```

```{r}
dhist <- cleandhist(dhist)
dhist2 <- varandskew10(dhist)
head(dhist)


```


### Clean campattributes 

```{r}
#stuff in stringr 
#str_trim = trim leading and trailing white space 
#str_pad = pad with additional characters 
#str_detect = detects a pattern, returns TRUE/FALSE 
#str_replace = find and replace a pattern 
```

```{r}
getdigits <- function(string){
  list(regmatches(string,gregexpr("[[:digit:]]+\\.*[[:digit:]]*",string)))
}

cleanattributes <- function(dfatt){ 
  dfatt <- dfatt[ , -1]
  dfatt$goalamt <- gsub("'raised of", "", dfatt$goalamt,
     ignore.case = FALSE)
  dfatt$goalamt <- gsub("goal'", "", dfatt$goalamt,
     ignore.case = FALSE)
  dfatt$goalamt<- gsub("[[:punct:]]", "", dfatt$goalamt,  #yo you can also use str_replace if ya want
     ignore.case = FALSE)
  dfatt$amtraised<- gsub("[[:punct:]]", "", dfatt$amtraised,
     ignore.case = FALSE)
  dfatt$goalamt <- as.integer(dfatt$goalamt)
  dfatt$amtraised <- as.integer(dfatt$amtraised)
  dfatt$terminatedbool <- str_detect(dfatt$terminated, "donations")
  dfatt$nonprofit <- str_detect(dfatt$nonprofit., "Registered")
  dfatt<- dfatt%>% mutate(progress = amtraised/goalamt) %>% rename(urlsolid = urlname)
}


```

```{r}
campatt <- cleanattributes(campatt)
nrow(campatt)
```

#Merge important parts of dhist and campatt

```{r}
dfc <- left_join(dhist, campatt, by = "urlsolid")
dfc <- dfc %>% select(-verified, -description1, -description2, -description3, -nonprofit.)
```



